Test parsing of Proff.no table

### 2022-07-14 Test parsing of Proff table.Rmd
Visualisations.

@@

## New function - ffs
```{r}
read_proff6 <- function(file, start, end){
  require(rvest)
  require(tidyverse)
  require(janitor)
  read_html(file, encoding = "UTF-8") |> 
  html_node("#inner-frame") |> 
  html_table() |> 
  select( # removing empty column
    REGNSKAPSPERIODE:all_of(start)) |> # using all_of()
  mutate( # removing whitespace
    REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
  ) |> 
    filter( # removing duplicate table - no idea why it's necessary
      !row_number() > 176
    ) |>
  filter( # removing duplicate rows
    !grepl("Lukk", REGNSKAPSPERIODE)
    ) |> 
  pivot_longer( # tidying data
    all_of(end):all_of(start), names_to = "year") |> # using all_of()
  mutate( # changing to real NAs and turning years into numbers
    value = na_if(value, "-"),
    year = as.integer(year)) |> 
  mutate( # adding currency column
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |> 
  fill( # filling the currency column
    valutakode, .direction = "updown"
    ) |> 
  filter( # removing dates and redundant currency
    REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
      REGNSKAPSPERIODE != "Valutakode") |> 
  mutate( # removing whitespace in numbers
    value = str_replace_all(value, "\\s", "")
  ) |> 
  mutate( # turning into numbers
    value = as.numeric(value)
  ) |> 
  mutate( # removing years as values
    value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
  ) |> 
  mutate( # values no longer in 1000
      value = value * 1000
    ) |> 
  distinct() |> # removing duplicate rows
  pivot_wider( # pivoting
      names_from = REGNSKAPSPERIODE, values_from = value
      ) |> 
  clean_names() |> # tidying names
  select(-lederlonn_i_hele_1000,
           -resultatregnskap_i_hele_1000,
           -balanseregnskap_i_hele_1000) |> # removing headings
  rename( # making it clear what lonn refers to
      lederlonn = lonn
    ) |> 
  arrange(desc(year)) # arranging by year
}

read_proff6("Links/Kors.html", "2001", "2020")
read_proff6("Links/opera.html", "1998", "2021")
read_proff6("Links/Riksmaal.html", "2011", "2021")

@@

>>>>

`read_proff6` is the current leading contender...

@@

## New function - ffs
```{r read_proff6}
read_proff6 <- function(file, start, end){
  require(rvest)
  require(tidyverse)
  require(janitor)
  read_html(file, encoding = "UTF-8") |> 
  html_node("#inner-frame") |> 
  html_table() |> 
  select( # removing empty column
    REGNSKAPSPERIODE:all_of(start)) |> # using all_of()
  mutate( # removing whitespace
    REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
  ) |> 
    filter( # removing duplicate table - no idea why it's necessary
      !row_number() > 176
    ) |>
  filter( # removing duplicate rows
    !grepl("Lukk", REGNSKAPSPERIODE)
    ) |> 
  pivot_longer( # tidying data
    all_of(end):all_of(start), names_to = "year") |> # using all_of()
  mutate( # changing to real NAs and turning years into numbers
    value = na_if(value, "-"),
    year = as.integer(year)) |> 
  mutate( # adding currency column
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |> 
  fill( # filling the currency column
    valutakode, .direction = "updown"
    ) |> 
  filter( # removing dates and redundant currency
    REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
      REGNSKAPSPERIODE != "Valutakode") |> 
  mutate( # removing whitespace in numbers
    value = str_replace_all(value, "\\s", "")
  ) |> 
  mutate( # turning into numbers
    value = as.numeric(value)
  ) |> 
  mutate( # removing years as values
    value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
  ) |> 
  mutate( # values no longer in 1000
      value = value * 1000
    ) |> 
  distinct() |> # removing any remaining duplicate rows
  pivot_wider( # pivoting
      names_from = REGNSKAPSPERIODE, values_from = value
      ) |> 
  clean_names() |> # tidying names
  select(-lederlonn_i_hele_1000,
           -resultatregnskap_i_hele_1000,
           -balanseregnskap_i_hele_1000) |> # removing headings
  rename( # making it clear what lonn refers to
      lederlonn = lonn
    ) |> 
  arrange(desc(year)) # arranging by year
}

read_proff6("Links/Kors.html", "2001", "2020")
opera <- read_proff6("Links/opera.html", "1998", "2021")
read_proff6("Links/Riksmaal.html", "2011", "2021")

@@

## Function 6 visualisations
```{r}
ggplot(opera, aes(year, lederlonn)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "", big.mark = ".",
                                                   decimal.mark = ","))
opera |> 
  group_by(year) |> 
  transmute(
    sum = sum(lederlonn, leder_annen_godtgjorelse, na.rm = TRUE)
  ) |> 
  ggplot(aes(year, sum)) +
  geom_col()
opera
opera_lonn <- opera |> 
  group_by(year) |> 
  transmute(
    sum = sum(lederlonn, leder_annen_godtgjorelse, na.rm = TRUE) / arsresultat,
    profit = ifelse(arsresultat >= 0, TRUE, FALSE)
  ) |> 
  ggplot(aes(year, sum, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_percent(scale = 1),
                     name = "Godtgjørelse") +
  xlab("År") +
  theme(legend.position = "none")

opera_lonn
ggplotly(opera_lonn)
```
